---
title: "Challenges"
author: Henry Schubert
output: bookdown::html_document2
bibliography: "../my_references.bib"

---

```{r setup, include=FALSE  }
knitr::opts_chunk$set(echo = FALSE)
```

# Challenge Funktion



```{r }
library(mytestpkg)
```


Reproducible research is important for scientific community [@marwick2017computational].Otherwise @roth2016short show the opportunity.And @bellwald2008hydraulic 


This is a test function to test the fn:  `r Chal_func(15)`

In table \@ref(tab:summarycars) you can see
```{r summarycars}
knitr::kable(head(summary(cars)),  caption = "Summary of cars")
library(binford)
data(LRB)
knitr::kable(head(LRB))
checkpoint::checkpoint("2017-07-20")
```

In Figure \@ref(fig:pressureplot) you can clearly see an increase...
```{r pressureplot, fig.cap="The pressure of"}
plot(pressure)
```

This is the function 
```{r , echo = TRUE}
Test_func <- function(x){
  k = x^2
  return(k)
}
Test_func(10)
Chal_func(5)
```

If x = 5 the result is `r Chal_func(5)`. And  should be `r number_er(3)`. Good calculations!

Neuer Text



# References

<!--         
1. Within you ms, add a simple table and plot
2. Add captions and cross refs to those
3. Add a bib file & two citations to your ms
4. Add a second simple function to your R
5. Add a simple test for this send fn
6. Have you pkg pass the test

neue Funtionen immer in einer R-Datei speichern und 


-->

