---
title: "Challenges"
author: Henry Schubert
output: bookdown::html_document2
bibliography: "../my_references.bib"

---

```{r setup, include=FALSE  }
knitr::opts_chunk$set(echo = FALSE)
```

# Challenge Funktion



```{r }
library(mytestpkg)
```


Reproducible research is important for scientific community [@marwick2017computational].Otherwise @roth2016short show the opportunity.And @bellwald2008hydraulic 



In table \@ref(tab:summarycars) you can see
```{r summarycars}
knitr::kable(head(summary(cars)),  caption = "Summary of cars")
library(binford)
data(LRB)
knitr::kable(head(LRB))
```

In Figure \@ref(fig:pressureplot) you can clearly see an increase...
```{r pressureplot, fig.cap="The pressure of"}
plot(pressure)
```

This is the function 
```{r , echo = TRUE}
Test_func <- function(x){
  k = x^2
  return(k)
}
Test_func(10)
```

Good calculations!

Neuer Text

# Point Patter
```{r point pattern}
harran <- read.table("../data/Sites_HarranPlain.csv", sep = ",", header=TRUE)
#str(harran)

```

# Spatstat
```{r}
library(sp)
coordinates(harran) <- ~X+Y
#str(harran)
proj4string(harran) <- CRS("+init=epsg:4326")

#str(harran)
harran <- spTransform(harran, CRSobj = CRS("+init=epsg:32637"))

library(spatstat)
harran_ppp <- ppp(x = harran@coords[,1],
                  y = harran@coords[,2], 
                  window = owin(xrange = harran@bbox[1,],
                                yrange = harran@bbox[2,])
                  )

harran_ppp <- ppp(x = harran@coords[,1],
                  y = harran@coords[,2], 
                  window = owin(xrange = harran@bbox[1,],
                                yrange = c(min(harran@coords[,2]),
                                           min(harran@coords[,2]+60000))))

## harran_ppp <- ppp(x = harran@coords[,1],
                  #y = harran@coords[,2], 
                  #window = owin(xrange = harran@bbox[1,],
                                #yrange = c(min(harran@coords[,2]),
                                           #min(harran@coords[,2]+60000))), check = FALSE)

#str(harran_ppp)
plot(harran_ppp)
```

# challenge: delete duplicated points
```{r chi}
## Löschen der Punkte, entweder in obere Funktion check = FALSE einbauen, oder die unteren beiden Funktion
anyDuplicated(harran_ppp)
harran_ppp <- unique.ppp(harran_ppp)
# oder
harran_ppp <- harran_ppp[!duplicated(harran_ppp)]

# Nearest Neighbor Distance
harran_ppp_nn <- nndist(harran_ppp)
#str(harran_ppp_nn)

# Verschiedene Dartellungsmöglichkeiten Boxplot 
boxplot(harran_ppp_nn)
# sortierte Barplots
barplot(sort(harran_ppp_nn))
# Histogramm
hist(harran_ppp_nn)
```

# Challenge: create kernel density estimation

```{r ch2}
# Kernel density estimation, sigma = Bandwidth
harran_kde <- density.ppp(harran_ppp, sigma = mean(harran_ppp_nn))
plot(harran_kde)

# Um das sigma zu finden, Hypothese Daten eher First order Structure
# bw.ppl - Likelihood Cross Validation Bandwith Selection for Kernel Density
bw.ppl(harran_ppp)
plot(bw.ppl(harran_ppp))
plot(bw.ppl(harran_ppp), xlim = c(2000, 5000))
# Daten eher Second order Structure - geclustert
# bw.diggle - Cross Validation Bandwith Selection for Kernel Density
bw.diggle(harran_ppp)
```

Are our density of point location depends on the elevation?

# Raster
```{r}
# Raster importieren mit Paket Raster 
library(raster)
dem <- raster("../data/dem.tif")
# Für spatstat muss das Raster importiert werden
im_dem <- as.im(as.image.SpatialGridDataFrame(as(dem, "SpatialGridDataFrame")))

# andere Möglichkeit mit Paket rgdal
# library(rgdal)
# dem <- readGDAL("../data/dem.tif")
# hist(dem@data$band1)

```

# Challenge: rhohat
```{r}
# Intensity as Function of a Covariate 
harran_rhohat <- rhohat(object = harran_ppp,
                        covariate = im_dem,
                        bw = 200)
plot(harran_rhohat, xlim = c(350,600))

# Simuliert eine Dichte nur anhand der Höhe
rho_dem <- predict(harran_rhohat)
plot(rho_dem)

# Difference zwischen der Dichte durch Kernel Estimation und die simulierte Dichte
diff_rho <- harran_kde - rho_dem
plot(diff_rho)

# Create random points with rpoissp function that have the same intensity like our point pattern
# Random Poisson - vollkommend zufällige Verteilung
# set.seed sagt dem Computer, wo er anfangen soll, daher ergibt sich immer das gleiche zufällige Ergebnis
set.seed(123)
test2 <- rpoispp(harran_ppp$n/area.owin(harran_ppp$window), 
                           win = harran_ppp$window)
# andere Variante
set.seed(123)
test3 <- rpoispp(intensity(harran_ppp), win=Window(harran_ppp))
# einfache Variante
set.seed(123)
test4 <- rpoispp(ex = harran_ppp)

plot(harran_ppp)
points(test2, col = "green")
points(test3, col = "red")
points(test4, col = "blue")

```

# Second order effects
```{r}
# G-Function compare nearest neighbor (r-radius, km-empirical data)
harran_g <- Gest(harran_ppp)
str(harran_g)
# pois - zufällige Verteilung (pois), clustered beim starken Anstieg über der Kurve
# Gbord, Ghan Edge-Effect herausgerechnet
plot(harran_g)

# berechnet Random Points und für diese die G-Function
harran_ge <- envelope(harran_ppp, fun = "Gest")
plot(harran_ge)

# F-Function 
harran_f <- Fest(harran_ppp)
plot(harran_f)
harran_fe <- envelope(harran_ppp, fun = "Fest")
plot(harran_fe)

# K-Function
harran_k <- Kest(harran_ppp)
plot(harran_k)
harran_ke <- envelope(harran_ppp, fun = "Kest")
plot(harran_ke)

harran_kinhom <- envelope(harran_ppp, fun = "Kinhom")
```

When the black line is out of the grey range, the points are clustered.

```{r}
harran_gi <- Ginhom(harran_ppp, lambda = predict(harran_rhohat))
plot(harran_gi)
```

# References

<!--         
1. Within you ms, add a simple table and plot
2. Add captions and cross refs to those
3. Add a bib file & two citations to your ms
4. Add a second simple function to your R
5. Add a simple test for this send fn
6. Have you pkg pass the test

neue Funtionen immer in einer R-Datei speichern und 


-->

